Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/related.tex
added bernhard sok

%Related Work
The \BRAVO audit \cite{bravo} is the most popular ballot polling audit. When ballots are sampled one at a time, it is the audit with the smallest expected number of ballots drawn.

@@

Where \BRAVO uses the ratio of the values of the conditional probability distributions, \Minerva uses the ratio of their \emph{tails}.

>>>>

%Related Work
Bernhard provides a good description of the RLA and its assumptions, and also describes the process on the ground \cite{bernhard-sok}.

The \BRAVO audit \cite{bravo} is the most popular ballot polling audit. When ballots are sampled one at a time, it is the audit with the smallest expected number of ballots drawn.

@@

Where \BRAVO uses the ratio of the values of the probability distribution functions, \Minerva uses the ratio of their \emph{tails}.
